disturbance chronologies

### 2017-06-02 analysis/analysis_disturbance_chronos.Rmd
update disturbance chronos

```{r}

gc_caL <- computeGC(caL_tree, ws=10, prefijo = 'CA')
gc_caH <- computeGC(caH_tree, ws=10, prefijo = 'CA')
gc_sj <- computeGC(sj_tree, ws=10, prefijo = 'SJ')

>>>>

```{r}
gc_caL <- computeGC(caL_tree, ws=10, prefijo = 'CA')
gc_caH <- computeGC(caH_tree, ws=10, prefijo = 'CA')
gc_sj <- computeGC(sj_tree, ws=10, prefijo = 'SJ')

# mean by year 
# dataframe for plot 
gc_todos <- c()

datasetes <- c('gc_caL', 'gc_caH', 'gc_sj')

for (d in datasetes){ 
  # get df
  df <- get(d)

  aux_df <- df %>%
    group_by(year) %>% 
    summarise(ntrees = length(tree),
              gc_m = mean(gc_mean),
              gc_m_sd = sd(gc_mean),
              gc_m_se = sd(gc_mean) / sqrt(n()), 
              gc_md = mean(gc_median),
              gc_md_sd = sd(gc_median),
              gc_md_se = sd(gc_median) / sqrt(n())) %>%  
    mutate(site=paste(d))

  gc_todos <- rbind(gc_todos, aux_df)
}

gc_todos %>% ggplot(aes(x=year, y=gc_m)) + 
  geom_bar(stat='identity', fill='gray', colour='gray') + theme_bw() + 
  # geom_point() +
  geom_errorbar(aes(ymin = gc_m - gc_m_se, ymax = gc_m + gc_m_se), colour='gray') +
  facet_wrap(~site, nrow = 3, scales = 'free_y',
             labeller=as_labeller(c('gc_caH' = 'Canar High', 
                                 'gc_caL' = 'Canar Low',
                                 'gc_sj' = 'San Juan'))) +
  geom_hline(yintercept=c(25, -25), linetype=2, colour='blue') +
  geom_hline(yintercept=c(50, -50), linetype=2, colour='red') + 
  ylab('Mean GC') + 
  theme(panel.grid.minor = element_blank(), 
        strip.background = element_rect(colour='black', 
                                        fill='white'))

## Númber of trees 
GC_trees <- function(gcdf, treshold){

  th <- as.numeric(treshold)

  # Get total tree by year 
  n_tree <- gcdf %>% group_by(year) %>% summarise(total_tree = length(ntrees))

  # Get n tree with GC positve upper treshold 
  n_pos <- gcdf %>% filter(gc_m > th) %>% group_by(year) %>% summarise(n_pos = length(ntrees))

  # Get n tree with GC negative lower treshold 
  n_neg <- gcdf %>% filter(gc_m < (-1*th)) %>% group_by(year) %>% summarise(n_neg = length(ntrees))

  # Join and compute percentage 
  outgc <- n_tree %>% 
    left_join(n_pos, by='year') %>% 
    left_join(n_neg, by='year') %>% 
    mutate(per_pos = round((n_pos / total_tree) * 100, 2),
         per_neg = round((n_neg / total_tree) * 100, 2))

  return(outgc)
}

treesth <- GC_trees(gcdf = gc_todos, treshold = 50)

t_caL <- gc_todos %>% filter(site == 'gc_caL') %>% 
  GC_trees(treshold = 50) %>% data.frame()
t_caL$site <- 'gc_caL'

t_caH <- gc_todos %>% filter(site == 'gc_caH') %>% 
  GC_trees(treshold = 50) %>% data.frame()
t_caH$site <- 'gc_caH'

t_sj <- gc_todos %>% filter(site == 'gc_sj') %>% 
  GC_trees(treshold = 50) %>% data.frame()
t_sj$site <- 'gc_sj'

per_t <- rbind(t_caH, t_caL, t_sj)

per_t %>% ggplot(aes(x=year, y=gc_m)) + 
  geom_bar(stat='identity', fill='gray', colour='gray') + theme_bw() + 
  # geom_point() +
  geom_errorbar(aes(ymin = gc_m - gc_m_se, ymax = gc_m + gc_m_se), colour='gray') +
  facet_wrap(~site, nrow = 3, scales = 'free_y',
             labeller=as_labeller(c('gc_caH' = 'Canar High', 
                                 'gc_caL' = 'Canar Low',
                                 'gc_sj' = 'San Juan'))) +
  geom_hline(yintercept=c(25, -25), linetype=2, colour='blue') +
  geom_hline(yintercept=c(50, -50), linetype=2, colour='red') + 
  ylab('Mean GC') + 
  theme(panel.grid.minor = element_blank(), 
        strip.background = element_rect(colour='black', 
                                        fill='white'))

# EOBS data climate

xx %>% group_by(year, gc_mean) %>% count(tree) %>% filter(gc_mean > 50)

p %>% filter(site=='sj') %>% 
  ggplot(aes(x=year, y=mgc_md)) + 
  geom_bar(stat='identity') + theme_bw() + 
  # facet_wrap(~site, nrow = 3, scales = 'free_y') +
  geom_hline(yintercept=c(25, -25), linetype=2, colour='blue') +
  geom_hline(yintercept=c(50, -50), linetype=2, colour='red')

gc_caH %>% 
  group_by(year) %>% 
  summarise(nt = length(tree),
            mgc = mean(gc)) %>% 
  ggplot(aes(x=year, y=mgc)) + geom_bar(stat='identity') + theme_bw() + 
  geom_hline(yintercept=c(25, -25), linetype=2, colour='blue') +
  geom_hline(yintercept=c(50, -50), linetype=2, colour='red')

gc_sj %>% 
  group_by(year) %>% 
  summarise(nt = length(tree),
            mgc = mean(gc)) %>% 
  ggplot(aes(x=year, y=mgc)) + geom_bar(stat='identity') + theme_bw() + 
  geom_hline(yintercept=c(25, -25), linetype=2, colour='blue') +
  geom_hline(yintercept=c(50, -50), linetype=2, colour='red')

# + ylim(c(-300,300))
